---
title: "Homework 2"
author: "Joe Stoica"
date: "9/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(tidyverse)
library(ggthemes)
library(scales)
```

```{r data and global constants}
cytof <- read_csv("cytof.csv")
blue <- "#6093ca"
```

### 1. Convert the dataset from wide to long form as we did in class. 

```{r}
gathered_cytof <- cytof %>% 
  gather(key = "marker", value = "value")
```

####Make a faceted plot showing the distributions of each of the markers and describe these distributions. 

```{r}
gathered_cytof %>% 
  ggplot(aes(x = value)) + 
  geom_histogram(fill = blue) + 
  facet_wrap(.~marker, nrow = 7) + 
  theme_fivethirtyeight() + 
  theme(axis.title = element_text()) +
  xlab("Value") + 
  ylab("Density") + 
  ggtitle("Densities of CyTOF Markers") + 
  scale_x_continuous(breaks = seq(0, 10, 5)) + 
  scale_y_continuous(breaks = seq(0, 2, 1))
```


These distributions show a few things:
1. There are multiple markers exhibiting bimodality, with the higher peak usually
appearing on the left side of the histogram.
2. There are multiple histograms showing unimodal behavior, which may be suggestive
of being normally distributed observations. 

#### What features do you notice? Are there groups of markers that seem more similar to each other?

The markers that begin with CD seem to be either bimodal with left peaks or unimodal.
There is only one KIR marker (KIR2DL5) that is not bimodal. The NK marker class seems
to have the highest number of unimodal distributions. Essentially, markers in the
same class seem to usually have similar distributions to one another. 

***

### 2. Choose two of the markers and make a Q-Q plot comparing their distributions. 

```{r}
markers <- gathered_cytof %>% 
  filter(marker %in% c("CD56", "CD69"))

markers %>% 
  ggplot(aes(sample = value)) +
  stat_qq()
```

What is the relationship between the distributions? 

Can you describe it as a simple shift, or is it something more complicated?

Is it different for different parts of the distribution?





*** 

3.Compute some summary statistics of the markers, describing their center, spread, or any
other relevant features you can think of. Plot these statistics and interpret what your results.
How do you like these plots compared with the plots of the full distribution?


```{r}
cytof_summary <- gathered_cytof %>% 
  group_by(marker) %>% 
  summarise(med = median(value),
            mean = mean(value),
            sd = sd(value)) %>% 
  as.tibble()


cytof_summary %>% arrange(med)


cytof %>% 
  ggplot(aes(factor(marker), value)) + 
  geom_boxplot()
  
```



*** 