---
title: "Mini Project 2"
author: "Joe Stoica, Conor Devins"
date: "10/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(tidyverse)
library(ggbiplot)
```

```{r, message=FALES, warning=FALSE}
members1989 <- read_csv("congress/1989/members.csv")
votes1989 <- read_csv("congress/1989/votes.csv") 
members2014 <- read_csv("congress/2014/members.csv")
votes2014 <- read_csv("congress/2014/votes.csv") 
```

##Polarization in two years
### Take a look at the voting records for one of the earlier sessions in the dataset and one of the later sessions Using either PCA on the senators by bills matrix or multi-dimensional scaling on a measure of distance between senators that you construct, make a plot describing the relationships between the senators. Does it look like they fall on a one-dimensional liberal/conservative axis?  Are there outliers?  Are the patterns similar in the two years that you chose? What are the differences in the PCA/MDS plots in the two years that you chose?

```{r}
## this makes members and votes go in the same order
joined_1989 = join(members1989, votes1989, by = "id")
new_votes_1989 = joined_1989[,c(-1, -2, -3, -4, -5, -6)]
new_members_1989 = joined_1989[,1:6]

## Decide how to recode the variables
## this function maps "Yea" to 1, "Nay" to -1, everything else to 0
recode = function(x) {
  if(is.na(x)) {
    return(0)
  } else if(x == "Yea") {
    return(1)
  } else if(x == "Nay") {
    return(-1)
  } else {
    return(0)
  }
}

votes_recoded_1989 = apply(new_votes_1989, 1:2, recode)

prcomp1989 = prcomp(votes_recoded_1989, scale. = FALSE)

biplot1989 <-  ggbiplot(prcomp1989, scale = 0, var.axes = FALSE, group = new_members_1989$party)  +
  scale_color_manual(values = c("D" = "darkblue", "R" = "firebrick", "I" = "green")) + 
  labs(title = "PCA on US Political Party Senate Votes in 1989",
       x = "PC1",
       y = "PC2")
```




```{r}
## this makes members and votes go in the same order
joined = join(members2014, votes2014, by = "id")
new_votes_2014 = joined[,c(-1, -2, -3, -4, -5, -6)]
new_members_2014 = joined[,1:6]

## Decide how to recode the variables
## this function maps "Yea" to 1, "Nay" to -1, everything else to 0
recode = function(x) {
  if(is.na(x)) {
    return(0)
  } else if(x == "Yea") {
    return(1)
  } else if(x == "Nay") {
    return(-1)
  } else {
    return(0)
  }
}

votes_recoded_2014 = apply(new_votes_2014, 1:2, recode)

prcomp2014 = prcomp(votes_recoded_2014, scale. = FALSE)

biplot2014 <- ggbiplot(prcomp2014, scale = 0, var.axes = FALSE, group = new_members_2014$party)  +
  scale_color_manual(values = c("D" = "darkblue", "R" = "firebrick", "I" = "Green")) +
  labs(title = "PCA on US Political Party Senate Votes in 2014",
       x = "PC1",
       y = "PC2")
```

```{r}
biplot1989
```

Here we can see two distinct clusters of Democrats and Republicans. Both groups 
appear to have similar variance in their "long" direction, while the Democrats
have a little more spread in the middle than the Republicans. There appears to be 
a clear diviison in the middle, however some Senators do come relatively to each other.

```{r}
biplot2014
```

This is the PCA biplot for the 2014 U.S. Senate votes. This is very different from
1989's biplot. The Democrats are very tightly clustered, suggesting that they 
all have similar voting patterns. There is one outlier though, and it seems that 
the Independent partys vote like Democrats do. The Republicans, however, are very 
spread out and although they form a distinct cluster, their voting behavior varies 
may more than then Democrats.


It is apparent that there is a definite increase in polarization between 1989 and 2014 
due to the fact the two clusters are much further apart.


***

## Polarization over time
### Next, we want to look at this more systematically over time.  Repeat the same analysis you used in the first part for every year in our dataset.   Construct a measure  describing  polarization,  and  plot  it  over  time  (think  about  variance  explained, average distance between the scores for Democrats and Republicans, or similar measures). If you are able to make a clean visualization showing the PCAs or MDSs for each session of congress and you think it helps to support your claims, include that as well. Do you think that polarization has increased over time?  Is something more complicated happening?  Back up your claim with specific aspects of your analyses and graphs, and describe why they support your claim.



Ideological position of one senator
The analyses in the previous parts told us about the relative
ideological positions of and the amount of separation between the parties, but not about
absolute changes from year to year. We might want to know about absolute changes in the
ideological positions of the parties so that we can assign blame to one or both parties for
polarization, but it’s a tricky question to get at because both the senators voting on the bills
and the bills being voted on change from year to year.
One way of starting to answer the question is to take one senator who served each year and
compare the parties to that senator.  If the senator’s politics stayed the same over time, we
can measure the two parties’ positions relative to that senator.
On the other hand, if you think that there hasn’t been an increase in polarization and that
the ideological distributions of the parties has stayed basically the same over time, we can
investigate whether individual senators have changed their politics over time in the same
way, by measuring the position of a given senator relative to the positions of the two major
parties.

Choose one senator who served in all (or at least many) of the years we have represented in
our dataset, and make a plot describing his or her position relative to the two major parties
over time.  Describe the implications of your plot either in terms of which party is more
to blame for polarization or relating to the question of whether that senator’s politics has
changed over time. You should also describe the limitations of your analysis, and whether
there are other possible explanations for the phenomena you see.

Note:
An example of a senator whose ideology we might expect to have been constant over
time is Mitch McConnell (currently the majority leader and a senator from Kentucky).  A
senator whose ideology we might suspect has changed over time is John McCain, the late
senator from Arizona.
Grading


: Submit a report as a PDF, the body of which should be no more than ten pages, including
graphs (if you don’t feel like you need ten pages, submit fewer). Additional technical graphs can
be included in an appendix, which will not count toward the ten page limit and which we might
not bother to read.  Submit your code as a separate file.  Also upload any additional sources
required to reproduce your work.
Point distribution:

–
10
points for the first set of questions.
–
10
points for the second set of questions.
–
10
points for the third set of questions.
–
10
points for presentation.