---
title: "EDA Homwork 4"
author: "Joe Stoica, Conor Devins"
date: "10/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(tidyverse)
library(broom)
```

```{r}
df <- read_csv("data.csv")
```

Using loess or otherwise, fit a model to predict log10 (budget) from year and length.  For
simplicity, do not transform year and length (even though a transformation of length would
probably be sensible.) You will have to make a number of modeling choices:


#### Should you fit a linear or curved function for year and/or length?

```{r}
pairs(log(df$budget) ~ df$year + df$length)
```
#TODO DOUBLE CHECK THIS IS HOW YOU DO THIS HAHA

We will fit a curved function for length due to it appearing to have a slightly 
curved shape that appears to violate linear assumptions. A linear fit seems more 
appropriate for year, however, because it doesn't appear to be curved.  

***

#### Do you need an interaction between year and length?

```{r}
make_coplot_df = function(data_frame, faceting_variable, number_bins = 6) {
  ## co.intervals gets the limits used for the conditioning intervals
  intervals = co.intervals(data_frame[[faceting_variable]], number = number_bins)
  ## indices is a list, with the ith element containing the indices of the
  ## observations falling into the ith interval
  indices = apply(intervals, 1, function(x)
    which(data_frame[[faceting_variable]] <= x[2] & data_frame[[faceting_variable]] >= x[1]))
  ## interval_descriptions is formatted like indices, but has interval
  ## names instead of indices of the samples falling in the index
  interval_descriptions = apply(intervals, 1, function(x) {
    num_in_interval = sum(data_frame[[faceting_variable]] <= x[2] & data_frame[[faceting_variable]] >= x[1])
    interval_description = sprintf("(%.2f, %.2f)", x[1], x[2])
    return(rep(interval_description, num_in_interval))
  })
  ## df_expanded has all the points we need for each interval, and the
  ## 'interval' column tells us which part of the coplot the point should
  ## be plotted in
  df_expanded = data_frame[unlist(indices),]
  df_expanded$interval = factor(unlist(interval_descriptions),
                                levels = unique(unlist(interval_descriptions)), ordered = TRUE)
  return(df_expanded)
}

df_cond_on_year = make_coplot_df(df, "year", 10)
df_cond_on_length = make_coplot_df(df, "length", 10)

ggplot(df_cond_on_year, aes(y = budget, x = length)) +
  geom_point() +
  facet_wrap(~ interval, ncol = 5) +
  geom_smooth(method = "loess", se = FALSE, span = 1, method.args = list(degree = 1)) +
  ggtitle("Coplot of Budget ~ Length given Year") + 
  scale_x_continuous(breaks = seq(0,400,200))
```

The coplot shows that there is a clear interaction between year and budget because there are very distinct differences as time passes, so we will include it in the model. 

***

#### What span should you use in your loess smoother?

```{r fitted vs resid}
ggplot(m1_df, aes(x = .fitted, y = .resid)) +
  geom_point() + 
  stat_smooth(method = "loess", method.args = list(degree = 1, family = "symmetric"), se = TRUE) + 
  geom_hline(yintercept = 0, col = "red")
```

```{r, include=FALSE}
ggplot(m2_df, aes(x = .fitted, y = .resid)) +
  geom_point() + 
  stat_smooth(method = "loess", method.args = list(degree = 1, family = "symmetric"), se = TRUE) + 
  geom_hline(yintercept = 0, col = "red")

ggplot(m3_df, aes(x = .fitted, y = .resid)) +
  geom_point() + 
  stat_smooth(method = "loess", method.args = list(degree = 1, family = "symmetric"), se = TRUE) + 
  geom_hline(yintercept = 0, col = "red")
```

We chose a span of 0.1, because the residuals seem to be centered around 0 the most here. 
If we were to do this more formally, we would use cross validation to find a span
that minimizes mean square error.  

***

#### Should you fit using least squares or a robust fit?
#TODO EXPLAIN MORE, GRAPH?
We chose to use a robust fit since it is less prone to the outliers that are present
in this dataset. 

***

```{r, include=FALSE}
# Span 
m1 <- loess(log(budget) ~ year + length + year*length, data = df,
            drop.square = "year",
            family = "symmetric",
            degree = 2, 
            span = 0.1)

m1_df = augment(m1)

m2 <- loess(log(budget) ~ year + length + year*length, data = df,
            drop.square = "year",
            family = "symmetric",
            degree = 2, 
            span = 0.25)

m2_df = augment(m2)

m3 <- loess(log(budget) ~ year + length + year*length, data = df,
            drop.square = "year",
            family = "symmetric",
            degree = 2, 
            span = 0.5)

m3_df = augment(m3)
```


```{r}
# year residuals
ggplot(m1_df, aes(x = year, y = .resid)) +
  geom_point(alpha = 0.2) +
  stat_smooth(method = "loess", 
              method.args = list(degree = 1, family = "symmetric"))+
  geom_hline(yintercept = 0, col = "red")

# length residuals
ggplot(m1_df, aes(x = length, y = .resid)) +
  geom_point(alpha = 0.2) +
  stat_smooth(method = "loess", 
              method.args = list(degree = 1, family = "symmetric"))+
  geom_hline(yintercept = 0, col = "red")

# coplot condition on year
m1_df_cond_on_year = make_coplot_df(m1_df, "year", 10)

ggplot(m1_df_cond_on_year, aes(y = .resid, x = length)) +
  geom_point() +
  facet_wrap(~ interval, ncol = 5) +
  geom_smooth(method = "loess", se = FALSE, span = 1, method.args = list(degree = 1, family = "symmetric")) +
  ggtitle("Coplot of Budget ~ Length given Year") + 
  scale_x_continuous(breaks = seq(0,400,200))

# coplot condition on length
m1_df_cond_on_length = make_coplot_df(m1_df, "length", 10)

ggplot(m1_df_cond_on_length, aes(y = .resid, x = year)) +
  geom_point() +
  facet_wrap(~ interval, ncol = 5) +
  geom_smooth(method = "loess", se = FALSE, span = 1, method.args = list(degree = 1, family = "symmetric")) +
  ggtitle("Coplot of Budget ~ Length given Year") + 
  scale_x_continuous(breaks = seq(0,400,200))

# fitted vs residuals 
ggplot(m1_df, aes(x = .fitted, y = .resid)) +
  geom_point() + 
  stat_smooth(method = "loess", method.args = list(degree = 1, family = "symmetric"), se = TRUE) + 
  geom_hline(yintercept = 0, col = "red")

## qqplot of residuals
m1_df %>% 
  ggplot(aes(sample = .resid)) + 
  stat_qq() + 
  stat_qq_line()
```


–
Draw  one  set  of  faceted  plots  to  display  the  fit  –  either  condition  on  year  or  length,
whichever seems to you to be more interesting. Choose a sensible number of panels. Briefly
describe what this set of plots shows you.
–
# TODO
Draw a raster-and-contour plot (or other "3D" plot of your choice) to further display your
fit.  Briefly describe what, if anything, this plot shows you that your plot for question 2 didn’t.

What to submit:
–
An R code file to reproduce your fit and plots.
–
A write-up containing:
–
The line of R code you used to produce your loess model.
–
A justification of your modeling choices.
–
Two graphs and brief comments on those two graphs.  (You should draw many more
than two graphs when deciding what model to fit, but only include two graphs in
your submission.)

