---
title: "EDA Homework 3"
author: "Joe Stoica, Conor Devins"
date: "9/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lattice)
library(ggthemes)
load("lattice.RData")
```

We'll try transfomations and modeling of the food web data, described in Cleveland starting on page 58.

It is available in the lattice.RData file, which you can download from http://ml.stat.purdue.edu/stat695t/R/lattice.RData.

The data set is called food.web, and it contains two variables  
  -- mean.length, a positive, continuous variable giving the average length of the food web, and  
  -- dimension, a categorical variable taking values Mixed, Two, and Three, giving the type of food web.  
We will be interested in how mean.length varies with dimension.


####1. Make a Q-normal plot of mean.length, faceted out by dimension. 

```{r}
head(food.web)

food.web %>% 
  ggplot(aes(sample = mean.length)) + 
  stat_qq() +
  facet_grid(. ~ dimension, space = "free_y") + 
  theme_fivethirtyeight() +
  theme(axis.title = element_text()) +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Q-Normal Plots for the Food Web by Dimension") + 
  NULL
```

Are the data well described by a normal distribution?

#### 2. Let's try some transformations of mean.length. Make Q-normal plots of log-transformed mean.length and power-transformed mean.length, with power -1 (so the inverse transfor- mation), faceted out by dimension.

```{r}
lm(data = food.web, mean.length^-1 ~ factor(dimension))
```

Do either of these transformations make mean.length look more normally distributed?

#### 3. Let's model the inverse of mean.length as a function of dimension. Create a linear model with the inverse of mean.length as the response (y variable) and dimension as the predictor (x variable).

```{r}
mod <- lm(mean.length^-1~0+dimension, data=food.web)
summary(mod)
```

As dimension increases from Two to Mixed to Three, the mean of the inverse of mean length decreases from 0.426 to 0.372 to 0.307.

```{r}
qqnorm(resid(mod))
abline(0, .1)
```

The Q-Normal plot shows that the pooled residuals of the model conform very closely to a normal distribution, with a slightly heavy tail at the lower end of the distribution.

